\documentclass[letter,10pt]{article}
\usepackage{ds_resume}
\begin{document}

%====================
% PrecisionLender / Q2 - Senior Data Engineer
%====================
\subsection{{Senior Data Engineer \hfill Aug 2019 --- Present}}
\subtext{Q2 \hfill Cary, NC - Remote}

\vspace{10pt}

Senior member of Data Engineering team with experiences ranging from ETL job writing, to infrastructure development, to project planning, and mentoring.

\vspace{10pt}

\skills{Responsibilities}
\begin{zitemize}
    \item Managed ETL for Data Engineering and Data Science for the benefit of two company products, amounting to approximately 50,000 job instances, nightly. Powered by Airflow, running both python and pyspark jobs.
    \item Led a proof-of-concept, planned a migration, and implemented a seamless transition from an Azure-based ETL to a Kubernetes-based solution to improve execution environment flexibility and scaling. (From Azure Data Factory, Batch, and Databricks to Airflow on Kubernetes with a mix of Celery, K8sPod, and Spark on Kubernetes jobs).
    \item Inherited and automated a suite of ETL processes used to support and enable business monitoring and reporting operations for a newly acquired business unit.
    \item Contributed to the migration of a fraud detection product from a legacy on-premise monolithic application to a series of cloud-based serverless microservices in order to improve resiliency and accuracy, while reducing operational cost.
    \item Utilized code reviews, requests for discussions (RFDs), documentation, and project proposals as teaching opportunities for fellow technical peers on the importance of strong communication skills in a technical career.
    \item Served as volunteer for a company-wide, quarterly, Squad Health Check program to provide teams a space for guided reflection on intra- and inter-team interactions as a means of identifying risks and successes, as well as setting goals for iterative improvement.
\end{zitemize}

\vspace{5pt}
\vspace{5pt}

%====================
% Republic Wireless - Data Engineer
%====================
\subsection{{Data Engineer \hfill Jun 2015 --- Aug 2019}}
\subtext{Republic Wireless \hfill Raleigh, NC}

\vspace{10pt}

Owner of internal data warehouse and associated ETL processes used by all departments to derive business insights.

% Report to Sr. Director of Software Development

\vspace{10pt}

\skills{Responsibilities}
\begin{zitemize}
    \item Owned, managed, and developed internal corporate AWS Redshift data warehouse structure, views, and associated Python ETL processes. Warehouse contained 50+ billion rows across $\sim$700 tables, processing $\sim$10k queries per day.
    \item Developed software and processes for internal data movement, manifesting as prototyped applications, ingress data pipelines, and egress data distribution.
    \item Implemented data integrity processes through outlier detection for advanced warnings of ETL or data source corruption.
    \item Answered complex business questions by translating requirements into programmatic logic, through the development of tools, using Python and SQL.
    \item Managed AWS resource instantiation, configuration, security, and deployment.
    \item Administered internal data visualization platform, Periscope Data, and fulfilled reporting requests.
    \item Mentored peers on topics and best practices in data modeling, ETL, SQL querying, and Python development.
\end{zitemize}

\vspace{5pt}

% Removed "Key Projects" section when adding Q2 content
% \skills{Key Projects}
% \begin{zitemize}
%     \item (In Progress) Member Usage Metric Data Store Replacement - develop real-time member usage data ingestion, storage, retention, and access abstraction (API) to replace a legacy system and reduce its operational cost.
%     \item Data Warehouse Consolidation and Transfer of Ownership - seamlessly consolidated and simplified Operations’ data warehouses and ETL libraries into Engineering-managed and monitored ecosystem for improved accuracy, efficiency, and stability.
%     \item Data Warehouse Ingestion Evolution - implemented structural consistency and dependency management through unification of custom ETL processes into Python, using Spotify’s Luigi pipeline framework -- led to role as Luigi Contributor and Maintainer.
%     \item Prototype and Beta Test of SMS Chatbot Support Service - developed and evaluated SMS-based support chatbot to improve quality and speed of two-way support communications.
% \end{zitemize}

\end{document}
